Photosynthesis Course Note

### 2016-07-16 Draft/draft.tex
Adding notes for sheaf cohomology. Updating the notes for "light harvesting system". Updating notes for Q.F.T.

@@

    The $\Lambda$ and $\Lambda^{-1}$ can be determined by several 
    equations that relate it with $\eta_{\mu\nu}$. Note that:
    $$ \Lambda^{\rho}_{ \nu} \neq \Lambda^{ \rho}_\nu$$
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.

>>>>

\usepackage{tensor}  % For tensor indices
\usepackage[all]{xy} % For drawing category diagrams
\usepackage{mathrsfs}

@@

    The $\Lambda$ and $\Lambda^{-1}$ can be determined by several 
    equations that relate it with $\eta_{\mu\nu}$.

    Note that:
    \[ \Lambda\indices{^\rho_\nu} \neq \Lambda\indices{_\nu^\rho} \]
    And:
    \begin{equation}
        \label{eq:2.3_Quantum_Lorentz_Transformations transformation_matrix}
        (\Lambda^{-1})\indices{^\rho_\nu} = 
            \Lambda\indices{_\nu^\rho} = 
            \eta_{\nu\mu}\eta^{\rho\sigma} \Lambda\indices{^\mu_\sigma}
    \end{equation}

    The only part about quantum mechanics here, is that the operators
    corresponding to the Lorentz transformations, have the property that:
    \begin{equation}
        U(\bar\Lambda,\bar{a})U(\Lambda, a) = 
            U(\bar\Lambda\Lambda, \bar\Lambda a + \bar{a})
    \end{equation}
    where $a$ represents the translation.

    The group of Lorentz transformations is very important. There is:
        %\text{sssssss} & B
    \[
        \xymatrix{ 
        \text{Poincar\'e Group}  \\
        \text{Homogeneous Lorentz group} \ar@{^{(}->}[u] \\
        \text{proper orthochronous Lorentz group}\ar@{^{(}->}[u]
        }
    \]
    The important \textit{proper orthochronous Lorentz group} consists
    of those $\Lambda$ with $\det \Lambda = 1$ and 
    $\Lambda\indices{^0_0} \geq 1$.

    We have also $ \mathscr{P}$, the space inversion matrix. And
    \(\mathscr{T}\), the time-reversal matrix. The definition for
    both can be easily written.

    A important rule is that all homogeneous Lorentz transformations can
    are generated by 
    \(\{\text{proper orthochronous}, \mathscr{P}, \mathscr{T} \}\).
    However this property is not proved

    \paragraph{Digression about tensor notation} It seems that phsysicists
    have not settled down on their notation for tensors. Weinberg using
    the notation $\Lambda\indices{^\nu_\mu} \equiv \Lambda(e^\nu,e_\mu)$,
    so it acts on $(v,w)$, where $v$ is a cotangent vector and $w$ is a
    tangent vector. I see that this notation helps to distinguish the
    type of arguments. This is unnecessary, since the upper and lower
    indices already fulfill this function. Another benefit is that it
    conveies the process of lowering of raising a index.

    However, this idea that each slot in tensor indices are distinct
    and can be lowered and raised seperatly, is not even mentioned
    in some modern mathematical physics book.

    Helpful link:
    \href{http://physics.stackexchange.com/questions/158309/convention-of-tensor-indices}{Convention of tensor indices in Phy.SE}, and 
    \href{http://physics.stackexchange.com/questions/237270/working-with-indices-of-tensors-in-special-relativity?noredirect=1&lq=1}{Working with indices of tensors in special relativity in Phy.SE}.

\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.

### 2016-07-16 Light harvesting/Photosynthesis Course Note.tex
Adding notes for sheaf cohomology. Updating the notes for "light harvesting system". Updating notes for Q.F.T.

\abstract{
    This is a note of the course \textit{An Introduction
    to Light Harvesting in Bacteria and Plants}. The course is more
    of a research than of a pedagodic taste: ideas and
    methods are only mentioned, with reference to the published paper
    available in the corresponding slides.
    Therefore, this note aims to provide a guidance to read those slides.
    Note that the page numbers in this note are the page numbers of
    each individual PDF, not necessarily the page numbers displayed
    on the bottom-right corner inside the PDFs.
}
\section{June 29th}
\label{sec:June_29th}

@@

\section{July 1th}
\label{sec:July_1th}
Begin with a review of two modes of excitons in organic system
\textbf{pp.1}, this
lecture proceeds to explain in detail the dipole interaction potential
(\textbf{pp.2 to 3})
$V_{uv}$ mentioned in previous lecture. \textbf{Page 4 to 5} digresses on
the difference between the transition dipole moment and the
permanent dipole moment. On page 4, the picture shows the transition dipole
moment for a Bacteriacholorophyll (the photosynthetic pigments that 
occur in various phototrophic bacteria). The right side plot illustrates
the absorption spectra for Bacteriacholorophyll. Page 5 originally
contains an animated display, which is lost in this PDF file, although
the content is not important.
\textbf{Page 6 and 7} also digresses on eletronic momenta and oscillator
strength.

@@

\section{July 6th}
\label{sec:July_6th}
This lecture begins with a note on the unbelievable efficiency of biological
system. Then it proceeds to review some concepts in quantum statistical 
mechanics ( \textbf{page 2 to 21}). Since we are quite familar with this
subject, it will be omitted from this note. The last page mentioned an
important equation for the evolvement of density matrix in an open system,
called the "master equation".
% TODO reference required!

\section{July 8th}
\label{sec:July_8th}
In the previous lecture, the \textit{master equation} for density matrix
\footnote{Reference not found.}
could lead to problematic result. When the density matrix propagates
as described by the master equation, the eigenvalues for it might
evolve into comprising negative values. This is because the added terms
are not rigorously derived, but just an approximation. On \textbf{page 2} the
teacher mentioned a specific case.\footnote{
    Digression: in the article PRE 65 056120, we can find
    something about the entanglement between two oscillators.
}
Therefore, one introduces the \textbf{Lindblad equations}
(\textbf{pp.3}). This equation ensures that the 
density matrix $\rho \geq 0$ (i.e. having all positive
eigenvalues). However, this operator sometimes breaks down
the symmetries of the system. That is, a system started with
translation symmetry at $t_0$ might not have translation
symmetry at $t > t_0$.

@@

\section{July 13th}
\label{sec:July_13th}

@@

Next we write out the Hamiltonian for the LH1/2. (\textbf{pp.26})
The phonon $H_{ph}$ term 
contains 16 phonons for 16 pigments in LH1. The exciton term $H_{ex}$
assumes that the interaction is only nearst neighbour interaction.
The exciton-phonon interaction $H_{\text{ex-ph}}$ is essentially
the usual electron-phonon interaction term in solid state physics.
\section{July 15}
\label{sec:July_15}

% $q$ represent the phonon vibration. Since $\Omega(Q) = \Omega(0) = 
% \frac{\partial}{\partial q}q + ...$, the linear-diagonal coupling
% is just the first.
% $\gamma_{mn}^l$, $\gamma_0$ is the energy for the phonon on the same
% site. 
Here we first introduces a new term in the Hamiltonian, 
$H_{\text{ex-ph}}^{\text{off-diagonal}}$.

Taking a linear approximation of the phonon band. We will find
a Hunag-Rhys factor $S$ in $\sum_q g_q^2 \omega_q = S\omega_0$.

We will use a time-dependent variational calculation. Then
we introduces a Davydov ansatz. Note that
\begin{align*}
    e^{A+B} = e^A e^B e^{\frac{1}{2}[A,B]}
\end{align*}
% todo check this
And using this relationship, it could be found that the $\ket{\beta}$
is actually a Glauber coherent state.

note that the Davydov ansatz is not translational invariant.

Next we project the Davydov ansatz into bloch states, and get
the Toyozawa's ansatz. This Toyozawa ansatz has a central
position. Using thise, we get the energy band.

@@

Shows a Holstein polaron's phase diagram. Outside the thin region,
there is always a unique solution (global minimum for the variational
parameters). Below the region, large polaron. Above, small polaron.
% todo what is a large polaron.
Inside the solid region, there will be two solutions coexisting.
The the solution obatined depeands on the initial configuration.
The physical picture is that, changing the value of $J$ and $g$,
the size of polaron will change sharply when one transverse the
dashed line.

Shows some variational parameters calculated. The strange wedge
in the picture, is the mode of $q=0$ mode ($\beta_{q=0} = g$). It is
called the Goldston mode, decoupled from the system. This explains
that the constant value inside these plots, when $q=0$.

When we calculate the off-diagonal coupling. There will be two
wedges

Then freqency plot. The labels are $(J,g,\phi)$, where $\phi$
is the off-diagonal strength.

Another approach, called the Munn-Silbey Method,
in which one first do a strange transformation
and 
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

>>>>

\abstract{
    This is a note of the course \textit{An Introduction
    to Light Harvesting in Bacteria and Plants}. The course is more
    of a research than of a pedagodic taste: ideas and
    methods are only mentioned, with reference to the published paper
    available in the corresponding slides.
    Therefore, this note aims to provide a guidance to read those slides.
    Note that the page numbers in this note are the page numbers of
    each individual PDF, not necessarily the page numbers displayed
    on the bottom-right corner inside the PDFs.
}
\section{June 29th Wed}
\label{sec:June_29th}

@@

\section{July 1th Fri}
\label{sec:July_1th}
Begin with a review of two modes of excitons in organic system
\textbf{pp.1}, this
lecture proceeds to explain in detail the dipole interaction potential
(\textbf{pp.2 to 3})
$V_{uv}$ mentioned in previous lecture. \textbf{Page 4 to 5} digresses on
the difference between the transition dipole moment and the
permanent dipole moment. On page 4, the picture shows the transition dipole
moment for a Bacteriacholorophyll (the photosynthetic pigments that 
occur in various phototrophic bacteria). The right side plot illustrates
the absorption spectra for Bacteriacholorophyll. Page 5 originally
contains an animated display, which is lost in this PDF file, although
the content is not important.
\textbf{Page 6 and 7} also digresses on eletronic momenta and oscillator
strength.

@@

\section{July 6th Wed}
\label{sec:July_6th}
This lecture begins with a note on the unbelievable efficiency of biological
system. Then it proceeds to review some concepts in quantum statistical 
mechanics ( \textbf{page 2 to 21}). Since we are quite familar with this
subject, it will be omitted from this note. The last page mentioned an
important equation for the evolvement of density matrix in an open system,
called the "master equation".
% TODO reference required!

\section{July 8th Fri}
\label{sec:July_8th}
In the previous lecture, the \textit{master equation} for density matrix
\footnote{Reference not found.}
could lead to problematic result. When the density matrix propagates
as described by the master equation, the eigenvalues for it might
evolve into comprising negative values. This is because the added terms
are not rigorously derived, but just an approximation. On \textbf{page 2} the
teacher mentioned a specific case.\footnote{
    Digression: in the article PRE 65 056120, we can find
    something about the entanglement between two oscillators.
}
Therefore, one introduces the \textbf{Lindblad equations}
(\textbf{pp.3}). This equation ensures that the 
density matrix $\rho \geq 0$ (i.e. having all positive
eigenvalues). However, this operator sometimes breaks down
the symmetries of the system. That is, a system started with
translation symmetry at $t_0$ might not have translation
symmetry at $t > t_0$.

@@

\section{July 13th Wed}
\label{sec:July_13th}

@@

Next we write out the Hamiltonian for the LH1/2. (\textbf{pp.26})
The phonon $H_{ph}$ term 
contains 16 phonons for 16 pigments in LH1. The exciton term $H_{ex}$
assumes that the interaction is only nearst neighbour interaction.
The exciton-phonon interaction $H_{\text{ex-ph}}$ is essentially
the usual electron-phonon interaction term in solid state physics.
\section{July 15, Friday}
\label{sec:July_15}

\textbf{Note}: In general, the difficulty in assimilation of ideas is
greater in Friday than in Wednesday's speech. I was lost again today.

Teacher first explains the Hamiltonian for off-diagonal coupling
(\textbf{pp.1 to 2}). (The off-diagonal represents phonon-exciton
interaction between different sites.)

Then he toke a linear approximation of the phonon band. He mentioned
a Hunag-Rhys factor $S$ in $\sum_q g_q^2 \omega_q = S\omega_0$.

\textbf{pp.4 to 7} reviews the traditional variational approach.

\textbf{pp.8} introduces the Davydov's ansatz.
Note that
\begin{align*}
    e^{A+B} = e^A e^B e^{\frac{1}{2}[A,B]}
\end{align*}
% todo check this
And using this relationship, it could be found that the $\ket{\beta}$
is actually a Glauber coherent state.

Note also that the Davydov ansatz is not translational invariant.

\textbf{pp.9} projects the Davydov ansatz into bloch states, and get
the Toyozawa's ansatz. This Toyozawa ansatz has a central
position. Using this, we get the energy band.

@@

\textbf{pp.10 }shows a Holstein polaron's phase diagram. 
\footnote{Could be found in pdf file "nonlocal.pdf".}
The region enclosed by the pointed solid line is of particular
interests. Outside this thin region,
there is always a unique solution (global minimum for the variational
parameters). 
% Below the region, large polaron. Above, small polaron.
% todo what is a large polaron.
Outside the region, there will be two solutions coexisting.
The the solution obatined depeands on the initial configuration.
The physical picture is that, changing the value of $J$ and $g$,
the size of polaron will change sharply when one transverse the
dashed line.

\textbf{pp.11} shows some results when only diagonal term
is considered.
\footnote{Could be found on "Toyozawa Ansat.pdf".}
The strange wedge
in the picture, is the mode of $q=0$ 
(in which case it could be found that $\beta_{q=0} = g$). 
It is
called the Goldstone mode. This mode is actually decoupled from 
the system, as can be found directly in the Hamiltonian. This explains
that the constant value inside these plots, when $q=0$.

\textbf{pp.13} is the result of off-diagonal coupling. 
% TODO reference not found
There will be two regions enclosed by solid line.

The remaining slides re not be included in this note,
since they follow the pattern of applying models developed
by condensed matter physicsists and showing the result.
Detailed results could be found in the papers provided by
the teacher.
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
